---
title: "SISBID day 2 code"
output: html_notebook
---

Installing google sheets
```{r}
library(devtools)
install_github("jennybc/googlesheets")
library(googlesheets)
```

Reading a google sheet

```{r}
sheets_url = "https://docs.google.com/spreadsheets/d/18KQQd4LY5k8Ucux1MvWCsQGQJlvd0ECTnn-3ixdOKFM/pubhtml"
gsurl1 = gs_url(sheets_url)
dat = gs_read(gsurl1)
date_accessed = date()
date_accessed
```


Look at the result

```{r lookatresult}
dat
```


Doing the lab

```{r}
aboutus = "https://docs.google.com/spreadsheets/d/103vUoftv2dLNZ_FcAz08b5ptIkWN4W2RaFn7VF39FJ8/edit#gid=0"
gsurl_about = gs_url(aboutus)
dat = gs_read(gsurl_about)
date_accessed = date()
date_accessed
```

Read just the first two columns
```{r}

dat2 = gs_read(gsurl_about,range=cell_cols(1:2))
dat2
```

Find out how many years of R experience

```{r}
dat = gs_read(gsurl_about)
dat
mean(as.numeric(dat$`Years of R experience`),na.rm=T)
logical_two_years = as.numeric(dat$`Years of R experience`) > 2
logical_two_years
```


## Doing JSON stuff now

Install stuff
```{r}
#install.packages("jsonlite")
library(jsonlite)
```


Read in JSON data

```{r}
github_url = "https://api.github.com/users/jtleek/repos"
jsonData <- fromJSON(github_url)
dim(jsonData)
names(jsonData)
jsonData$name
```


Exploring the data frame

```{r}
table(sapply(jsonData,class))
dim(jsonData$owner)
names(jsonData$owner)
jsonData$owner$html_url
```

Do the lab really quick

```{r}
github_url = "https://api.github.com/users/hadley/repos"
jsonData <- fromJSON(github_url)
```


Look at the names of the variables

```{r}
names(jsonData)
jsonData$stargazers_count
jsonData$open_issues
```
Safari -> preferences -> advanced -> checkbox "show development menu in menu bar"
Button on top where you can click "developer menu"

```{r}
install.packages("rvest")
library(rvest)
```


```{r}
recount_url = "http://bowtie-bio.sourceforge.net/recount/"
htmlfile = read_html(recount_url)
htmlfile
```


```{r}
nds = html_nodes(htmlfile,                
xpath='//*[@id="recounttab"]/table')
nds
```

```{r}
dat = html_table(nds)
dat = as.data.frame(dat)
head(dat)
names(dat) = dat[1,]
dat[-1,]
```


## APIs


Load the figshare package
```{r}
install.packages("rfigshare")
library(rfigshare)
```


Let's search for Jeff

```{r}
leeksearch = fs_search("Leek")
length(leeksearch)
leeksearch[[1]]
```

Install httr

```{r}
install.packages("httr")
library(httr)
```


GET data set

```{r}
query_url = "https://api.github.com/search/repositories?q=created:2014-08-13+language:r+-user:cran"
req = GET(query_url)
```


## Do the web scraping lab

Get the html file
```{r}
bioc_url = "https://raw.githubusercontent.com/SISBID/Module1/gh-pages/labs/bioc-software.html"
htmlfile = read_html(bioc_url)
htmlfile
```

Subset out the table
```{r}
nds = html_nodes(htmlfile,                
xpath='//*[@id="biocViews_package_table"]')
nds
```

Turn into a data frame

```{r}
dat = html_table(nds)
dat = as.data.frame(dat)
head(dat)
```


Get the text

```{r}
text = paste(dat[,3], collapse=" ")
text
```

Install wordcloud

```{r}
install.packages(c("wordcloud","tm"))
library(wordcloud)
```


Make the wordcloud

```{r}
wordcloud(text,max.words=50)
```



Do the api part

```{r}
oct4_dat = fromJSON("http://rest.ensembl.org//lookup/id/ENSG00000204531?content-type=application/json;expand=1")
str(oct4_dat)
```

Do the transcript part

```{r}
str(oct4_dat$Transcript)
```

Change genes
```{r}
newgene_dat = fromJSON("http://rest.ensembl.org//lookup/id/ENSG00000141510?content-type=application/json;expand=1")
str(newgene_dat)
```

Get the gene info at http://rest.ensembl.org/documentation/info/symbol_lookup.



Here is the example `/lookup/symbol/homo_sapiens/BRCA2?content-type=application/json;expand=1` and modify it with our gene like so: `/lookup/symbol/homo_sapiens/BRAF?content-type=application/json;expand=1`
We'd crete the url using the base url like this: `http://rest.ensembl.org//lookup/symbol/homo_sapiens/BRAF?content-type=application/json;expand=1`
We'd request the information with fromJSON

```{r}
braf_info = fromJSON("http://rest.ensembl.org//lookup/symbol/homo_sapiens/BRAF?content-type=application/json;expand=1")
braf_info$id
braf_info$display_name
```


```{r}
ids = c("ENSG00000157764","ENSG00000141510")
dat = vector(2,mode="list")
for(i in 1:2){
  base_url = "http://rest.ensembl.org//lookup/id/"
  tail_url = "?content-type=application/json;expand=1"
  url_want = paste0(base_url,ids[i],tail_url)
  dat[[i]] = fromJSON("http://rest.ensembl.org//lookup/id/ENSG00000141510?content-type=application/json;expand=1")
  Sys.sleep(2)
}
```

